---
title: "Bigram Relationships"
author: "Shannon Lo"
date: "19 Oct 2019"
output: html_document
---

```{r Load Dependencies, results='hide'}
library(tidyverse)
library(tidytext)
library(tm)
library(widyr)
library(igraph)
library(ggplot2)
library(ggraph)
library(readr)
library(tidygraph)
```

The following function(s) are defined below:
  * **visualize_bigrams**: extracts bigrams from a text field, calculates frequency of bigrams, and creates a bigram plot to visualize relationships between words
    + *df_name*: name of dataframe that contains the text field of interest
    + *textfield*: name of text field (ie. column name)
```{r Define Functions, results='hide'}
visualize_bigrams <- function(df_name, textfield){
  
    # Create frequencies of bigrams
    df_cleaned <- df_name %>% 
      mutate(textfield_clean = removeWords(gsub("[^A-Za-z0-9 ]", "", {{textfield}}), stop_words$word))
    
    df_bigrams <- df_cleaned %>%
      unnest_tokens(bigrams, textfield_clean, token = "ngrams", n = 2)
    
    df_freq <- as.data.frame(table(df_bigrams$bigrams)) %>% 
      arrange(desc(Freq))
    
    # Visualizations
    df_top_bigrams <- df_freq %>%
      top_n(100, Freq) %>% 
      separate(Var1, c("word1", "word2"))
    
    top_bigram_words <- c(df_top_bigrams$word1, df_top_bigrams$word2) %>%
      unique()
    
    word_list <- df_cleaned %>%
      unnest_tokens(words, textfield_clean, token = "ngrams", n = 1) 
    
    df_word_list <- as.data.frame(table(word_list$words)) %>% 
      arrange(desc(Freq)) %>%
      filter(Var1 %in% top_bigram_words)
    
    names(df_word_list)[2] <- "Term_Frequency"
    names(df_top_bigrams)[3] <- "Edge_Frequency"
    
    graph_from_data_frame(vertices =  df_word_list, d = df_top_bigrams) -> graph_hold
    
    graph_hold %>%
      ggraph(layout = "fr") +
      geom_edge_link(aes(edge_alpha = Edge_Frequency), show.legend = TRUE) +
      geom_node_point(aes(color = Term_Frequency, size = Term_Frequency), alpha = 0.7) +
      scale_fill_viridis_c() +
      geom_node_text(aes(label = name), repel = TRUE) +
      scale_color_viridis_c(direction = -1) +
      theme_void() + guides(size=FALSE) +
      title(main = {{title}})
    
}
```

Read in the following data sources:
  * **Web scraped data**: this CSV contains information on journals and was created using *database_parallel2.R*
  * **Topics and search terms**: this CSV contains 10 topics and 3 search terms for each topic
```{r Read Data, results='hide'}
# Read in web scraped data
df_raw <- read_csv("../data/AllWebscrape.csv") %>% 
  rename_all(tolower) %>% 
  rename(term = topic) %>% 
  mutate(term = str_to_lower(term))

# Read in topics and search terms data
search_terms <- read_csv("../raw-data/SearchTerms.csv") %>% 
  rename_all(tolower) %>% 
  mutate(term = str_to_lower(term))
```

Join journal and search term dataframes to get topics information by journals.

The topic for *global alignment sequence* and *read alignment sequence* is hard coded because the corresponding information in the search terms dataframe does not have the word "sequence", the topic cannot be joined by matching search terms.
```{r Transform Data, results='hide'}
df <- df_raw %>% 
  left_join(search_terms, by = "term") %>% 
  mutate(topic = ifelse(term %in% c("global alignment sequence", "read alignment sequence")
                        ,"Sequence Alignment"
                        ,topic))
```

Journals information is divided into 10 dataframes by topics. Visualizations can now we created by topic.
```{r Separate Data by Topics, results='hide'}
df_assembly <- df %>% 
  filter(topic == "Assembly")
df_databases <- df %>% 
  filter(topic == "Databases")
df_epigenetics <- df %>% 
  filter(topic == "Epigenetics")
df_geneexp <- df %>% 
  filter(topic == "Gene Expression")
df_genomeann <- df %>% 
  filter(topic == "Genome Annotation")
df_phylogenetics <- df %>% 
  filter(topic == "Phylogenetics")
df_seqal <- df %>% 
  filter(topic == "Sequence Alignment")
df_sequence <- df %>% 
  filter(topic == "Sequencing")
df_strucpred <- df %>% 
  filter(topic == "Structural Prediction")
df_varcall <- df %>% 
  filter(topic == "Variant Calling")
```

Create bigram plots to visualize the relationships between two words. The darker lines represent higher frequency of occurrence.
```{r Create Bigram Plots}
visualize_bigrams(df,abstract)
visualize_bigrams(df_assembly, abstract)
visualize_bigrams(df_databases, abstract)
visualize_bigrams(df_epigenetics, abstract)
visualize_bigrams(df_geneexp, abstract)
visualize_bigrams(df_genomeann, abstract)
visualize_bigrams(df_phylogenetics, abstract)
visualize_bigrams(df_seqal, abstract)
visualize_bigrams(df_sequence, abstract)
visualize_bigrams(df_strucpred, abstract)
visualize_bigrams(df_varcall, abstract)
```

