---
title: "Overview"
author: "Diana Lin"
date: "20/10/2019"
output: 
  html_document:
    toc: true
    theme: paper
---

```{r setup, include=FALSE, warning = FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = FALSE, message = FALSE, warning = FALSE, fig.width=12, fig.height=8)
```

## Set Up
Load all the necessary packages:
```{r load, warning= FALSE, message = FALSE}
library(future)
library(fulltext)
library(pubchunks)
library(tidyverse)
library(magrittr)
library(dplyr)
library(purrr)
library(here)
library(lubridate)
library(plotly)
library(scales)
library(stringr)
```

## Overview of Hits by Topic

Load all the search terms:
```{r}
searchTerms <- read_csv(here::here("/raw-data/SearchTerms.csv"))
searchTerms$Term %<>% as.character()
# searchTerms <- searchTerms %>% filter(Topic=="Sequence Alignment")
```

Set API keys:
```{r API keys, echo = FALSE}
Sys.setenv(ELSEVIER_SCOPUS_KEY = '3da3a9477a6e0a7fefc0bbfb49f288f5', SPRINGER_KEY = 'dc293398c185c33d930865ae1fd6eae3', ENTREZ_KEY = "1621b309cd4dab23f28c432d4e7baa76d909" )
```

Search for all search terms across all databases:
```{r overview}
resFound <- NULL

databaseList <- ft_search_ls()
# databaseList <- databaseList[!databaseList %in% c("bmc","scopus","entrez")]

for (t in unique(searchTerms$Topic)) {
    specific <- searchTerms %>% filter(Topic == t)
  for (st in specific$Term) {
    res1 <- ft_search(query = st,
                      from = databaseList,
                      limit = 10)
    
    for (nm in names(res1)) {
      Found <- res1[[nm]][["found"]]
      if (is.null(Found)) {
        Found <- 0
      }
      resFound <-
        bind_rows(resFound, data.frame(
          db = nm,
          found = Found,
          searchTerm = st,
          topic = t
        ))
    }
  }
}

resFound[resFound == 0] <- NA
resFound <- resFound %>% drop_na()

overview <- resFound %>%
  group_by(topic, db) %>%
  summarize(sum = sum(found)) %>%
  ggplot(aes(x = topic, y = sum)) +
  geom_col(aes(fill = db)) + 
  theme(axis.text.x = element_text(angle = 30),
        text = element_text(size = 20),
        axis.title = element_text(size =18),
        axis.text = element_text(size=12)
        ) +
  scale_y_continuous(label = scales::comma_format()) +
  labs(title = "Topic Overview Across Databases", y = "# Papers Found", x = "Topic", fill = "Database")
```

```{r, echo = FALSE}
print(overview)
```

```{r, echo = FALSE}
ggsave(here::here("figures", "overview.pdf"), height = 8, width =12, device = "pdf")
```

## Breakdown of Topic By Search Term

Plot the specific breakdowns in each topic:
```{r overview topic}
for (specific_topic in unique(searchTerms$Topic)) {
print(resFound %>%
  filter(topic == specific_topic) %>%
  mutate(searchTerm = str_replace_all(searchTerm, " ", "\n")) %>%
  group_by(searchTerm, db) %>%
  summarize(sum=sum(found)) %>%
  ggplot(aes(x = searchTerm, y = sum)) +
  geom_col(aes(fill = db)) +
  labs(title = specific_topic, y = "# Papers Found", x = "Search Terms", fill = "Database") +
  theme(text = element_text(size = 20),
        axis.title = element_text(size =18),
        axis.text = element_text(size=12),
       # axis.text.x = element_text(angle=20)
        ) +
    scale_y_continuous(label = scales::comma_format()))
}
```

### Breakdown of **Sequencing** By Search Term

Sequencing (specific):
```{r}
specific_topic <- "Sequencing"
resFound <- NULL

searchTerms <- read_csv(here::here("/raw-data/sequencing-specific.csv"))
searchTerms$Term %<>% as.character()

for (st in searchTerms$Term) {
  res1 <- ft_search(query = st,
                    from = databaseList,
                    limit = 10)
  for (nm in names(res1)) {
    Found <- res1[[nm]][["found"]]
    if (is.null(Found)) {
      Found <- 0
    }
    resFound <-
      bind_rows(resFound,
                data.frame(
                  db = nm,
                  found = Found,
                  searchTerm = st,
                  topic = specific_topic
                ))
  }
}

resFound[resFound == 0] <- NA
resFound <- resFound %>% drop_na()

sequencing_plot <- resFound %>%
#  filter(topic == specific_topic) %>%
  filter(searchTerm != "NGS",
       searchTerm != "third-generation sequencing",
       searchTerm != "ont reads sequencing") %>%
 # mutate(searchTerm = str_remove(searchTerm," sequencing")) %>%
 # mutate(searchTerm = str_remove(searchTerm, "sequencing ")) %>%
  mutate(searchTerm = str_remove(searchTerm, " sequencing")) %>%
  mutate(searchTerm = str_replace_all(searchTerm, " ", "\n")) %>%
  mutate(searchTerm = str_replace(searchTerm,"-", "\n")) %>%
  group_by(searchTerm, db) %>%
  summarize(sum=sum(found)) %>%
  ggplot(aes(x = searchTerm, y = sum)) +
  geom_col(aes(fill = db)) +
  labs(title = specific_topic, y = "# Papers Found", x = "Search Terms", fill = "Database") +
  theme(text = element_text(size = 20),
        axis.title = element_text(size =18),
        axis.text = element_text(size=12),
        axis.text.x = element_text(angle=30)
        ) +
    scale_y_continuous(label = scales::comma_format())
```

```{r, echo = FALSE}
print(sequencing_plot)
```

```{r, echo = FALSE}
ggsave(filename = here::here("figures", "sequencing.pdf"), plot = sequencing_plot, width = 12, height = 8, device = "pdf")
```


### Breakdown of **Assembly** By Search Term

Assembly (specific):
```{r}
specific_topic <- "Assembly"
resFound <- NULL

searchTerms <- read_csv(here::here("/raw-data/assembly-specific.csv"))
searchTerms$Term %<>% as.character()

for (st in searchTerms$Term) {
  res1 <- ft_search(query = st,
                    from = databaseList,
                    limit = 10)
  for (nm in names(res1)) {
    Found <- res1[[nm]][["found"]]
    if (is.null(Found)) {
      Found <- 0
    }
    resFound <-
      bind_rows(resFound,
                data.frame(
                  db = nm,
                  found = Found,
                  searchTerm = st,
                  topic = specific_topic
                ))
  }
}

# resFound$searchTerm <- as.factor(resFound$searchTerm)

resFound[resFound == 0] <- NA
resFound <- resFound %>% drop_na()

assembly_plot <- resFound %>%
#  filter(topic == specific_topic) %>%
 # mutate(searchTerm = str_remove(searchTerm," sequencing")) %>%
 # mutate(searchTerm = str_remove(searchTerm, "sequencing ")) %>%
  filter(searchTerm != "single cell assembly") %>%
  mutate(searchTerm = str_remove(searchTerm, " assembly")) %>%
  mutate(searchTerm = str_replace_all(searchTerm, " ", "\n")) %>%
  mutate(searchTerm = str_replace(searchTerm,"-", "\n")) %>%
  group_by(searchTerm, db) %>%
  summarize(sum=sum(found)) %>%
  ggplot(aes(x = fct_rev(fct_relevel(factor(searchTerm), levels = c("short read assembly", "long read assembly", "linked read assembly", "hybrid assembly", "scaffolding", "polishing", "single cell assembly"))), y = sum)) +
  geom_col(aes(fill = db)) +
  labs(title = specific_topic, y = "# Papers Found", x = "Search Terms", fill = "Database") +
  theme(text = element_text(size = 20),
        axis.title = element_text(size =18),
        axis.text = element_text(size=12),
        axis.text.x = element_text(angle=30)
        ) +
    scale_y_continuous(label = scales::comma_format())
```

```{r, echo = FALSE}
print(assembly_plot)
```

```{r, echo = FALSE}
ggsave(filename = here::here("figures", "assembly.pdf"), plot = assembly_plot, width = 12, height = 8, device = "pdf")
```


### Breakdown of **Sequence Alignment** By Search Term
Alignment (specific):
```{r}
specific_topic <- "Alignment"
resFound <- NULL

searchTerms <- read_csv(here::here("/raw-data/alignment-specific.csv"))
searchTerms$Term %<>% as.character()

for (st in searchTerms$Term) {
  res1 <- ft_search(query = st,
                    from = databaseList,
                    limit = 10)
  for (nm in names(res1)) {
    Found <- res1[[nm]][["found"]]
    if (is.null(Found)) {
      Found <- 0
    }
    resFound <-
      bind_rows(resFound,
                data.frame(
                  db = nm,
                  found = Found,
                  searchTerm = st,
                  topic = specific_topic
                ))
  }
}

resFound[resFound == 0] <- NA
resFound <- resFound %>% drop_na()

alignment_plot <- resFound %>%
#  filter(topic == specific_topic) %>%
 # mutate(searchTerm = str_remove(searchTerm," sequencing")) %>%
 # mutate(searchTerm = str_remove(searchTerm, "sequencing ")) %>%
  mutate(searchTerm = str_remove(searchTerm, " alignment")) %>%
  mutate(searchTerm = str_replace_all(searchTerm, " ", "\n")) %>%
  mutate(searchTerm = str_replace(searchTerm,"-", "\n")) %>%
  group_by(searchTerm, db) %>%
  summarize(sum=sum(found)) %>%
  ggplot(aes(x = searchTerm, y = sum)) +
  geom_col(aes(fill = db)) +
  labs(title = specific_topic, y = "# Papers Found", x = "Search Terms", fill = "Database") +
  theme(text = element_text(size = 20),
        axis.title = element_text(size =18),
        axis.text = element_text(size=12),
        axis.text.x = element_text(angle=30)
        ) +
    scale_y_continuous(label = scales::comma_format())
```

```{r, echo = FALSE}
print(alignment_plot)
```


```{r, echo = FALSE}
ggsave(filename = here::here("figures", "alignment.pdf"), plot = alignment_plot, width = 12, height = 8, device = "pdf")
```


