---
title: "Sankey Diagrams"
author: "Elliot YKF, Lucia Darrow"
date: "October 19, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r libraries}

library(data.table)
library(textrank)
library(udpipe)
library(dplyr)
library(tm)
library(tidytext)
library(stringr)
library(ggplot2)
library(magrittr)
library(plotly)
library(tidyverse)
library(googleVis)
library(ggrepel)
library(egg)
library(grid)
library(ggalluvial)

```


Read in the webscraped data and identify the top authors by publication count.

```{r import}

All <- read_csv("../data/AllWebscrape.csv")
All %>% group_by(author1,topic) %>% 
  summarise(count=n()) %>% 
  na.omit() %>% 
  arrange(desc(count)) -> authorTopic

# Remove NA values 
authorTopic %<>% na.omit() -> authorTopic
authorTopic <- authorTopic[authorTopic$author1!="NA, NA",]

# Get dataframe of the top authors and how many publications are from each topic area
authorTopic %>% 
  group_by(author1) %>% 
  summarise(count=sum(count)) %>% 
  arrange(desc(count)) -> TopAuthors

authorTopic %>% 
  filter(author1 %in% TopAuthors[1:10,]$author1) -> topAuthorTopics
```


Use the master search term file to get the list of topics to which each search term belongs. We will use the higher level topics for plotting in place of specific search terms.

```{r, getTopics} 
level <- read.csv("../raw-data/SearchTerms.csv")
level %<>% na.omit()
colnames(topAuthorTopics)[2] <- c("Term")
level$Term <- as.character(level$Term)
level$Term <- trimws(level$Term,"l")
topAuthorTopics$Term <- as.character(topAuthorTopics$Term)

topAuthorTopics$Term <- str_replace_all(topAuthorTopics$Term, " sequence","")
topAuthorTopics <- left_join(topAuthorTopics,level,by= "Term")

topAuthorTopics %>% group_by(author1,Topic) %>% summarise(count=sum(count)) %>% arrange(desc(count)) -> topAuthorTopics
```

Next, set up a Sankey flow diagram to display authors on the LHS (source) and topics on the RHS (sink). The weight of each connection represents the number of publications.

```{r, authorSankey}

datSK <- data.frame(From=c(as.character(topAuthorTopics$author1)),
                    To=(as.character(topAuthorTopics$Topic)),
                    Weight=topAuthorTopics$count)

# Joing to the publications by topic by author to get higher level publication counts
datSK %>% group_by(From) %>% 
  summarise(count=sum(Weight)) -> pubByAuthor
datSK <- left_join(datSK,pubByAuthor,by="From")

# Plot the sankey diagram using ggplot framework
sankey <- ggplot(datSK,
      aes(y = Weight, axis1 = From, axis2 = To)) +
 geom_alluvium(aes(fill=From), width = 1/12) +
 geom_stratum(alpha=0,width = 1/12, color = "black") +
 #geom_label(stat = "stratum", label.strata = TRUE,alpha=0.5, hjust=0.9) + 
  scale_x_discrete(limits = c("From", "To"), expand = c(0.3, 0.1)) +
  scale_fill_viridis_d() + 
  theme_void() + 
  theme(
    axis.title.y = element_blank(),
    axis.title.x=element_blank(),
    axis.ticks.x=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.x=element_blank(),
    axis.text.y=element_blank(),
    legend.position="none"
    ) + 
  ggrepel::geom_label_repel(aes(label=From),stat="stratum",size=3,direction="x",hjust=10) +
  ggrepel::geom_label_repel(aes(label=To),stat="stratum",size=3,direction="y",nudge_x = 0.5) +
  geom_label(aes(label=Weight),stat="stratum",alpha=0.8)
  
  
  
sankey <- set_panel_size(sankey,
                          width  = unit(18, "cm"),
                          height = unit(10, "cm"))
grid.newpage()
grid.draw(sankey)


```

Access the main webscraped data file and identify the top affiliations by publication count.

```{r topAffTopics}

# Group and summarize the data by affiliation to find the top institutions 
All %>% group_by(affiliation,topic) %>% 
  summarise(count=n()) %>% 
  arrange(desc(count)) -> affTrends
affTrends %<>% na.omit() -> affTrends

All %>% group_by(affiliation,topic) %>% 
  summarise(count=n()) %>% na.omit() %>% 
  arrange(desc(count)) -> affTopic

# Remove NA values
affTopic %<>% na.omit() -> affTopic

# Select the top ten institutions for further analysis
affTopic %>% group_by(affiliation) %>% 
  summarise(count=sum(count)) %>% arrange(desc(count)) -> TopAff
affTopic %>% filter(affiliation %in% TopAff[1:10,]$affiliation) -> topAffTopics

<<<<<<< HEAD
colnames(topAffTopics)[2] <- c("Term")


topAffTopics$Term <- str_replace_all(topAffTopics$Term, " sequence","")


topAffTopics <- left_join(topAffTopics,level,by="Term")


topAffTopics %>% group_by(affiliation,Topic) %>% summarise(count=sum(count)) %>% arrange(desc(count)) -> topAffTopics

# #Select Top 10
# topAffTopics <- topAffTopics[1:10,]
topAffTopics
```
```{r}
topAffTopics$affiliation <- gsub('Department of ', '', topAffTopics$affiliation)
topAffTopics$affiliation <- gsub('University of ', 'U ', topAffTopics$affiliation)
topAffTopics$affiliation <- gsub('United States of America', 'USA', topAffTopics$affiliation)
topAffTopics$affiliation <- gsub('University', 'U', topAffTopics$affiliation)

topAffTopics$affiliation <- gsub("(.)\n.+", "\\1", topAffTopics$affiliation)
gsub(".*, U ", "", topAffTopics$affiliation)


topAffTopics$affiliation <-str_replace_all(topAffTopics$affiliation,",","\n") 
topAffTopics$affiliation <- str_replace(topAffTopics$affiliation,"\n",",")
locationAfterN <- str_locate(topAffTopics$affiliation,"\n.+")


topAffTopics$affiliation <- str_sub(topAffTopics$affiliation,end=locationAfterN[,1]-1)
# str_replace(topAffTopics$affiliation,"\n*+.......",",")
topAffTopics$affiliation <-str_replace_all(topAffTopics$affiliation,",","\n") 
topAffTopics$affiliation

topAffTopics[str_detect(topAffTopics$affiliation,"U"),]

```


<!-- ```{r} -->

<!-- datSK <- data.frame(From=c(as.character(topAffTopics$affiliation)),To=(as.character(topAffTopics$Topic)),Weight=topAffTopics$count) -->

<!-- Sankey <- gvisSankey(datSK, from="From", to="To", weight="Weight", -->
<!--                      options=list( -->
<!--                        sankey="{link: {color: { fill: '#871b47' } }, -->
<!--                             node: { color: { fill: '#2A5E96' }, -->
<!--                             label: { color: '#000000'} }}")) -->
<!-- plot(Sankey) -->

<!-- library(ggalluvial) -->
<!-- is_alluvia_form(as.data.frame(datSK), axes = 1:3, silent = TRUE) -->


<!-- ggplot(datSK, -->
<!--       aes(y = Weight, axis1 = From, axis2 = To)) + -->
<!--  geom_alluvium(aes(fill=From), width = 1/12) + -->
<!--  geom_stratum(alpha=0.5,width = 1/12, color = "grey") + -->
<!--  geom_label(stat = "stratum", label.strata = TRUE,alpha=0.5) + scale_x_discrete(limits = c("From", "To"), expand = c(0.3, 0.1)) + -->
<!--  scale_fill_viridis_d() + theme_void() + theme(axis.title.y = element_blank(), -->
<!--     axis.title.x=element_blank(), -->
<!--     axis.ticks.x=element_blank(), -->
<!--     axis.ticks.y=element_blank(), -->
<!--     axis.text.x=element_blank(), -->
<!--     axis.text.y=element_blank(), -->
<!--     legend.position="none") -->



<!-- ``` -->
```{r}
datSK <- data.frame(From=c(as.character(topAffTopics$affiliation)),To=(as.character(topAffTopics$Topic)),Weight=topAffTopics$count) 

datSK %>% group_by(From) %>% 
  summarise(count=sum(Weight)) -> pubByAff
datSK <- left_join(datSK,pubByAff,by="From")

# Plot the sankey diagram using ggplot framework
sankey <- ggplot(datSK,
=======
```

Next, set up a Sankey flow diagram to display affiliations on the LHS (source) and topics on the RHS (sink). The weight of each connection represents the number of publications.

```{r affSankey}

datSK <- data.frame(From=c(as.character(topAffTopics$affiliation)),
                    To=(as.character(topAffTopics$topic)),
                    Weight=topAffTopics$count)

is_alluvia_form(as.data.frame(datSK), axes = 1:3, silent = TRUE)

ggplot(datSK,
>>>>>>> 4b8f66c45a4c9c9dab6b07a48edebda248ebe87c
      aes(y = Weight, axis1 = From, axis2 = To)) +
 geom_alluvium(aes(fill=From), width = 1/12) +
 geom_stratum(alpha=0,width = 1/12, color = "black") +
 #geom_label(stat = "stratum", label.strata = TRUE,alpha=0.5, hjust=0.9) + 
  scale_x_discrete(limits = c("From", "To"), expand = c(0.3, 0.1)) +
  scale_fill_viridis_d() + 
  theme_void() + 
  theme(
    axis.title.y = element_blank(),
    axis.title.x=element_blank(),
    axis.ticks.x=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.x=element_blank(),
    axis.text.y=element_blank(),
    legend.position="none"
    ) + 
  ggrepel::geom_label_repel(aes(label=From),stat="stratum",size=3,direction="x",hjust=10) +
  ggrepel::geom_label_repel(aes(label=To),stat="stratum",size=3,direction="y",nudge_x = 0.5) +
  geom_label(aes(label=Weight),stat="stratum",alpha=0.8) + ggtitle("")
  
  
  
sankey <- set_panel_size(sankey,
                          width  = unit(18, "cm"),
                          height = unit(10, "cm"))
grid.newpage()
grid.draw(sankey)
```

